\LARGE \bf WORKING TITLE: Incorporating User Feedback in Motion Planning for Manipulators

### 2014-09-29 paper2015asml.tex
more text for online survey

@@

The surveys were presented to users of Amazon Mechanical Turk, who would be presented with a set of demographic questions, a video, and the four scales to rate the robot's motion on the basis of elegance, efficency, smoothness and overall impression. Additionally a control question was presented with another video asking the participant about the robot's action in the accompanying video. This served as the first satisficing trap to ensure that participants were truthfully attempting the survey.

Each participant was allowed to provide feedback no more than once for each of the trajectories generated by the survey design.

\section{Survey Results}
The results of the survey are summarized in Fig.~\ref{fig:survey_raw} which shows a histogram of (average) responses for each of the four survey questions across the 100 trajectories that were rated by users. It is clear that a majority of the trajectories in our survey were well received by the human observers but there were quite a few trajectories that were rated badly as well. 
\begin{figure}[t]
  \centering{\includegraphics[width=\linewidth]{pictures/efficiency.pdf}}
  \centering{\includegraphics[width=\linewidth]{pictures/elegant.pdf}}
  \centering{\includegraphics[width=\linewidth]{pictures/smooth.pdf}}
  \centering{\includegraphics[width=\linewidth]{pictures/overall.pdf}}
  \caption{Histogram of averaged ratings for the 103 different trajectories. Clockwise from top left: Efficient vs. Inefficient, Elegant vs. Inelegant, Smooth vs. Rough, Overall Rating}
\label{fig:survey_raw}
\end{figure}

>>>>

\begin{figure}[b]
    \includegraphics[trim = 0mm 0mm 0mm 0mm, width=\columnwidth]{pictures/designing_queries_moveit}
    \caption{Screenshot of the planning query design process which involved hand-picking start and goal query poses for the various scenes manually to ensure they were neither trivial nor impossible for the planning algorithms to solve. This was accomplished through use of RVIZ and interactive markers.}
    \label{fig:design}
\end{figure}

After selecting the scenes, the robot was positioned in the scenes manually and planning queries were constructed by hand to reach a requisite number of planned trajectories~\ref{fig:design}. The positioning in the scenes was done with the expectation that the planning queries would not be impossible or trivial for the planning algorithms to solve.

Finally, the planning algorithms that were used were RRT-Connect~\cite{kuffner2000rrt}, and RRT*~\cite{frazzoli-RRTstar} with two cost functions: \emph{PathLength} and \emph{MaxMinClearance}.The objective for \emph{PathLength} minimizes the length of the trajectory (as the sum of the euclidean distances between ends of trajectory segments). The objective for \emph{MaxMinClearance} computes uses the minimum clearance of a configuration belonging to a trajectory as the value it is trying to maximize.

The library of trajectory videos was collected by computing plans with each of the previously discussed planners for the planning queries and scenes hand-picked from above. The plans were then recorded in simulation through RVIZ. In designing the online survey, these video recordings would be taken from multiple vantage points to maximize the visibility of the motion to the participant reviewing it.

@@

The surveys were presented to users of Amazon Mechanical Turk, who would be presented with a set of demographic questions, a video, and the four scales to rate the robot's motion on the basis of elegance, efficency, smoothness and overall impression. Additionally a control question was presented with another video asking the participant about the robot's action in the accompanying video. This served as the first satisficing trap to ensure that participants were truthfully attempting the survey. On overview of the main survey question can be seen in Figure~\ref{fig:survey_question}.

\begin{figure}
    \includegraphics[trim = 0mm 0mm 0mm 0mm, width=\columnwidth]{pictures/amazon_survey_screenshot}
    \caption{The main survey question which prompts the participant for a rating in four motion characteristics (efficiency, elegance, smoothness and overall impression) after presenting a video that demonstrates the motion from four clearly visible vantage points for any sample trajectory.}
    \label{fig:survey_question}
\end{figure}

Each participant was allowed to provide feedback no more than once for each of the trajectories generated by the survey design. We ran the survey for 103 trajectories, requesting no more than 20 ratings per trajectory. The analysis of these results will be done in Section~\ref{sec:analysis}.

\section{Survey Results}
\label{sec:analysis}
The results of the survey are summarized in Fig.~\ref{fig:survey_raw} which shows a histogram of (average) responses for each of the four survey questions across the 100 trajectories that were rated by users. It is clear that a majority of the trajectories in our survey were well received by the human observers but there were quite a few trajectories that were rated badly as well. 
\begin{figure}[t]
  \centering{\includegraphics[width=\linewidth]{pictures/efficiency.pdf}}
  \centering{\includegraphics[width=\linewidth]{pictures/elegant.pdf}}
  \centering{\includegraphics[width=\linewidth]{pictures/smooth.pdf}}
  \centering{\includegraphics[width=\linewidth]{pictures/overall.pdf}}
  \caption{Histogram of averaged ratings for the 103 different trajectories. Clockwise from top left: Efficient vs. Inefficient, Elegant vs. Inelegant, Smooth vs. Rough, Overall Rating}
\label{fig:survey_raw}
\end{figure}
